music

### 2020-02-17 analysis/02_DESeq2.Rmd
now with manipuation degs and modules of genes for music

```{r manipulation}
# import "colData" which contains sample information and "countData" which contains read counts
countData <- read.csv("../results/00_counts.csv", header = T, row.names = 1)
geneinfo <- read.csv("../metadata/00_geneinfo.csv", row.names = 1)
head(geneinfo)

@@

# craete variable that will be critical for subset later on
colData <- read.csv("../metadata/00_samples.csv", header = T, row.names = 1)
colData$sextissue <- as.factor(paste(colData$sex, colData$tissue, sep = "_"))
colData$treatment <- factor(colData$treatment, levels = manipulationsandcontrols)
colData$tissue <- factor(colData$tissue, levels = tissuelevel)
levels(colData$treatment)
levels(colData$sex)
levels(colData$sextissue)
levels(colData$tissue)
colData <- colData %>% drop_na()

@@

  # save differential gene expression results
  inc.d3.m.inc.d3 <- createDEGdfsaveManip("m.inc.d3", "inc.d3",  i) 
  inc.d9.m.inc.d9 <- createDEGdfsaveManip("m.inc.d9", "inc.d9",  i) 
  inc.d17.m.inc.d17 <- createDEGdfsaveManip("m.inc.d17", "inc.d17",  i) 
  hatch.m.n2 <- createDEGdfsaveManip("hatch", "m.n2",  i) 
  inc.d9.m.inc.d8 <- createDEGdfsaveManip("m.inc.d8", "inc.d9",  i) 
  inc.d17.prolong <- createDEGdfsaveManip("prolong", "inc.d17",  i) 
  hatch.extend <- createDEGdfsaveManip("extend", "hatch",  i) 
}

@@

>>>>

### Data wrangle

```{r manipulation1, include = F}
# import "colData" which contains sample information and "countData" which contains read counts
countData <- read.csv("../results/00_counts.csv", header = T, row.names = 1)
geneinfo <- read.csv("../metadata/00_geneinfo.csv", row.names = 1)
head(geneinfo)

@@

colData <- read.csv("../metadata/00_samples.csv", header = T, row.names = 1)
colData$sextissue <- as.factor(paste(colData$sex, colData$tissue, sep = "_"))
colData$treatment <- factor(colData$treatment, levels = manipulationsandcontrols)
colData$tissue <- factor(colData$tissue, levels = tissuelevel)
levels(colData$treatment)
levels(colData$sex)
levels(colData$sextissue)
levels(colData$tissue)
colData <- colData %>% drop_na()
```
### Manipuation: comparisons to respective controls

```{r manipulationcontrol, eval = F}

@@

  # save differential gene expression results
  inc.d3.m.inc.d3 <- createDEGdfsaveManip("m.inc.d3", "inc.d3",  i) 
  inc.d9.m.inc.d9 <- createDEGdfsaveManip("m.inc.d9", "inc.d9",  i) 
  inc.d17.m.inc.d17 <- createDEGdfsaveManip("m.inc.d17", "inc.d17",  i) 
  hatch.m.n2 <- createDEGdfsaveManip("m.n2", "hatch",  i) 
  inc.d9.m.inc.d8 <- createDEGdfsaveManip("m.inc.d8", "inc.d9",  i) 
  inc.d17.prolong <- createDEGdfsaveManip("prolong", "inc.d17",  i) 
  hatch.extend <- createDEGdfsaveManip("extend", "hatch",  i) 
}

@@

## Manipulation: comparisons to other manipluations

```{r manipulationwithin}
# import "colData" which contains sample information and "countData" which contains read counts
countData <- read.csv("../results/00_counts.csv", header = T, row.names = 1)
geneinfo <- read.csv("../metadata/00_geneinfo.csv", row.names = 1)
head(geneinfo)

colData <- read.csv("../metadata/00_samples.csv", header = T, row.names = 1)
colData$sextissue <- as.factor(paste(colData$sex, colData$tissue, sep = "_"))
colData$treatment <- factor(colData$treatment, levels = manipulationsandcontrols)
colData$tissue <- factor(colData$tissue, levels = tissuelevel)
levels(colData$treatment)
levels(colData$sex)
levels(colData$sextissue)
levels(colData$tissue)
colData <- colData %>% drop_na()

  # save differential gene expression results
  hatch.m.n2 <- createDEGdfsaveManip("m.n2", "hatch",  i) 
  prolong.extend <- createDEGdfsaveManip("extend", "prolong",  i) 
  early.extend <- createDEGdfsaveManip("extend", "m.inc.d8",  i) 
  early.prolong <- createDEGdfsaveManip("prolong", "m.inc.d8",  i) 
  m.inc.d9.m.inc.d3 <- createDEGdfsaveManip("m.inc.d9", "m.inc.d3",  i) 
  m.inc.d17.m.inc.d9 <- createDEGdfsaveManip("m.inc.d17", "m.inc.d9",  i) 
  m.inc.d17.m.inc.d3 <- createDEGdfsaveManip("m.inc.d17", "m.inc.d3",  i) 
  m.n2.m.inc.d17 <- createDEGdfsaveManip("m.n2", "m.inc.d17",  i) 
  m.n2.m.inc.d9 <- createDEGdfsaveManip("m.n2", "m.inc.d9",  i)
  m.n2.m.inc.d3 <- createDEGdfsaveManip("m.n2", "m.inc.d3",  i)
  prolong.m.inc.d17 <- createDEGdfsaveManip("prolong", "m.inc.d17",  i) 
  m.inc.d8.m.inc.d9 <- createDEGdfsaveManip("m.inc.d8", "m.inc.d9",  i) 
  extend.m.n2 <- createDEGdfsaveManip("extend", "m.n2",  i) 
}

### 2020-02-17 analysis/22_symphony.Rmd
now with manipuation degs and modules of genes for music

sinnermansong <- ggplot(sinnerman, aes(x = position, y = genes)) +
  geom_line(aes(color = music)) +
  geom_image(aes(image=image), size = 0.1) +
  scale_x_continuous(breaks = position,
                    labels = songstageslim,
                     name = element_blank()) +
  scale_y_continuous(breaks = c(3, 5, 7, 9),
                     labels = c( "F",   "A",   "C",  "E"),
                     limits = c(-1,12)) +
  geom_hline(yintercept=c(2.15,4.15,6.15,8.15,10.15))   +
  theme_B3() +
  theme(axis.ticks = element_blank()) +
  labs(subtitle = "Sinnerman by Nina Simone", y = NULL)
sinnermansong

```
```{r soulmusic}
p1 <- plot_grid(respectsong + theme(legend.position = "none"), feelinggoodsong + theme(legend.position = "none"), rel_widths = c(0.45,0.55))

p3 <- plot_grid(p1, sinnermansong, nrow = 2)
p3
```

@@

candidategenes <- c("PRL", "PRLR", 
                 "VIP", "VIPR1", "VIPR2", 
                 "OXT", "AVP", "AVPR1A", "AVPR1B", 
                 "GNRH1","GNRHR", "NPVF",
                 "NR3C1", "NR3C2",
                 "ESR1", "ESR2", "AR",
                 "DIO2","LEPR", "DIO3", "DIO1","CYP19A1",
                 "HSPA14", "HSPA12A",
                 "PTGES3", "HSD11B2","DRD5", "DRD1", "DRD2","PGE1", "PGF")

@@

d4 %>%
  filter( modulecolor != "turquoise",
          # modulecolor != "greenyellow",
          tissue == "pituitary") %>%
  droplevels() %>% 
    ggplot(aes(x = treatment, y = m)) +
  geom_image(aes(image=image), size = 0.15) +
  facet_wrap(~modulecolor, scales = "free_y", nrow = 2) +
  labs(subtitle = "WGCNA + canddiate genes in the pituitary", y = "gene expression", x = "parental stage") +
    facet_wrap(~gene, scales = "free_y", nrow = ) +
    theme_B3() +
    theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))

d4 %>%
  filter( modulecolor != "turquoise",
          # modulecolor != "greenyellow",
          tissue == "pituitary") %>%
  droplevels() %>% 
    ggplot(aes(x = treatment, y = m)) +
  geom_image(aes(image=image), size = 0.1) +
  labs(subtitle = "WGCNA + canddiate genes in the pituitary", y = "gene expression", x = "parental stage") +
    theme_B3() +
    theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_log10()

>>>>

sinnermansong <- ggplot(sinnerman, aes(x = position, y = genes)) +
  geom_line(aes(color = music)) +
  geom_image(aes(image=image), size = 0.1) +
  scale_x_continuous(breaks = position,
                    labels = songstageslim,
                     name = element_blank()) +
  scale_y_continuous(breaks = c(3, 5, 7, 9),
                     labels = c( "F",   "A",   "C",  "E"),
                     limits = c(-1,12)) +
  geom_hline(yintercept=c(2.15,4.15,6.15,8.15,10.15))   +
  theme_B3() +
  theme(axis.ticks = element_blank(),
        axis.text.x = element_text(angle = 10, hjust = 1)) +
  labs(subtitle = "Sinnerman by Nina Simone", y = NULL)
sinnermansong

```
```{r soulmusic}

p3 <- plot_grid(respectsong + theme(legend.position = "bottom"), 
                sinnermansong + theme(legend.position = "bottom"), 
                nrow = 1, rel_widths = c(0.45, 0.55))
p3
```

@@

candidategenes <- c("PRL", "PRLR", 
                 #"VIP", "VIPR1", "VIPR2", 
                 "OXT", "AVP",  "AVPR1B", # "AVPR1A",
                # "GNRH1","GNRHR", "NPVF",
                # "NR3C1", "NR3C2",
                # "ESR1", "ESR2",
                "AR",
                # "DIO2","LEPR", "DIO3", "DIO1","CYP19A1",
                # "HSPA14", "HSPA12A",
                # "PTGES3", "HSD11B2",
                 "DRD5", "DRD1", "DRD2",
                 #"PGE1", "PGF",
                 "BRCA1", "MYC", "PRKCZ" ,"FOSL2")

@@

turquoisegenes <- d4 %>%
  filter( modulecolor == "turquoise",
          tissue == "pituitary") %>%
  droplevels() %>% 
    ggplot(aes(x = treatment, y = m)) +
  geom_image(aes(image=image), size = 0.15) +
  geom_smooth(aes(x = as.numeric(treatment)), se = F, color = "turquoise") +
  facet_wrap(~modulecolor, scales = "free_y", nrow = 2) +
  labs(subtitle = "WGCNA turquoise module", 
       y = "gene expression  in the pitutiary", x = "parental stage") +
    facet_wrap(~gene, scales = "free_y", nrow = ) +
    theme_B3() +
    theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "italic"))

redgenes <- d4 %>%
  filter( modulecolor == "red",
          tissue == "pituitary") %>%
  droplevels() %>% 
    ggplot(aes(x = treatment, y = m)) +
  geom_image(aes(image=image), size = 0.15) +
  geom_smooth(aes(x = as.numeric(treatment)), se = F, color = "red") +
  facet_wrap(~modulecolor, scales = "free_y", nrow = 2) +
  labs(subtitle = "WGCNA red module", 
       y = "gene expression  in the pitutiary", x = "parental stage") +
    facet_wrap(~gene, scales = "free_y", nrow = ) +
    theme_B3() +
    theme(legend.position = "none", 
          axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "italic"))

turquoisegenes
redgenes

plot_grid(turquoisegenes, redgenes)
```

```{r}

d4 %>% 
  filter(gene %in% c("PRL", "PRLR", "ESR2")) %>%
ggplot( aes(x = treatment, y = m, color = gene)) +
    geom_smooth(aes(x = as.numeric(treatment)), se = F) +
    facet_grid(gene~tissue, scales = "free")

head(df)
head(df2)
```
